A Road Segment Prioritization Approach for Cycling Infrastructure

### 2021-05-08 arxiv.Rmd
arxiv tex file

---
title: A Road Segment Prioritization Approach for Cycling Infrastructure
#date: "`r Sys.Date()`"
geometry: margin=2cm
bibliography:
  - mybibfile.bib
  - rlbibfile.bib
#linenumbers: true
numbersections: true
abstract: "Understanding the motivators and deterrents to cycling is essential for creating infrastructure that gets more people to adopt cycling as a mode of transport. This paper demonstrates a new approach to support the prioritization of cycling infrastructure and cycling network design, accounting for cyclist preferences and the growing emphasis on 'filtered permeability' and 'Low Traffic Neighborhood' interventions internationally. The approach combines distance decay, route calculation, and network analysis methods to examine where future cycling demand is most likely to arise, how such demand could be accommodated within existing street networks, and how to ensure a fair distribution of investment. Although each of these methods has been applied to cycling infrastructure prioritization in previous research, this is the first time that they have been combined, creating an integrated road segment prioritization approach. The approach, which can be applied to other cities, as shown in the Appendix, is demonstrated in a case study of Manchester, resulting in cycling networks that balance directness against the need for safe and stress-free routes under different investment scenarios. A key benefit of the approach from a policy perspective is its ability to support egalitarian and cost-effective strategic cycle network planning. \\par\\textbf{Keywords:} cycling networks, low-traffic neighborhoods, routing, transport equity"
# keywords: "cycling networks, low-traffic neighborhoods, potential demand, routing"
output:
 # bookdown::github_document2:
   bookdown::pdf_document2:
 # bookdown::word_document2:
      highlight: null   # to remove code highlighting in r chunks
      toc: false
      extra_dependencies: ["subcaption", "longtable", "float", "multirow", "placeins", "multicol"]
editor_options:
  markdown:
    wrap: 72
# elsevier style for referencing (from https://github.com/citation-style-language/styles)
csl: elsevier-harvard.csl
always_allow_html: yes
---

@@

```{r, echo=FALSE, eval=FALSE}
file.rename("README.pdf", "cycle-network-paper.pdf")
```

@@

Much research has been done to understand what gets people to cycle.
Segregated cycling infrastructure^[*Segregated cycling infrastructure*
refers to road space that is allocated to cyclists only, with physical
separation to protect cyclists from other modes of transport.] has been
shown to increase cycling uptake [@aldred2019impacts; @goodman2014new;
@marques2015infrastructure], with the separation from motorized
vehicles being key [@winters2011motivators]. Revealed preference of
cyclists shows that they are willing to deviate from the most efficient
routes in order to commute on safer roads [@crane2017longitudinal].
However, such deviations are only considered if they do not considerably
increase route circuitry; behaviour studies have found that the
probability of choosing a route decreases in proportion to its length
relative to the shortest route [@broach2011bicycle; @winters2010far].
Another defining feature for cycling infrastructure is how well
connected it is. Cyclists prefer cohesive infrastructure, particularly
when cycling on arterial roads with high levels of motorized traffic
[@stinson2003commuter]. The lack of well-connected cycling
infrastructure is one of the main obstacles to increasing cycling uptake
[@caulfield2012determining]. While direct and cohesive cycling networks
have been shown to positively impact cycling rates, density^[making an
area's bicycle network denser means adding more cycling routes in the
area and thereby giving cyclists more route options.] of the cycling
network is also vital [@schoner2014missing].

@@

\noindent where $d$ and $s$ are the distance and slope associated with each
OD pair, and $\alpha$ and all $\beta$s, are parameters calculated by a regression
model on the training data. The square and square-root distance terms
"capture the non-linear impact of distance on the likelihood of
cycling", and interaction terms to capture the combined effect of slope
and distance [@lovelace2017propensity]. Alternative cycling uptake
models could be 'plugged in' to our approach for different contexts or scenarios of change.

@@

<!-- The difference between aggregate flow on weighted and unweighted networks is dependant on the road network of the city. Comparing Manchester to Nottingham, we see that trunk roads are much more important in the former, as over 25\% of flow on the unweighted road network passes through them. For Nottingham, less than 10\% of the flow on the unweighted network passes through trunk roads, but almost 25\% of the flow passes through tertiary roads (Figure \ref{fig:perc_person-km}).  -->

@@

This algorithm ensures that the resulting network is connected. It also
satisfies the directness criteria, since links on the weighted shortest
paths are those that have the highest flow passing through them (this is
a result of the routing in Section \@ref(introduction).

@@

Given that the "most essential activity entailed in the design of
cycle-friendly infrastructure is developing a cycle network"
[@parkin2018designing], we believe that the approach has great
potential to inform investment in cities such as Manchester where there
is political will to invest in cycling long-term. A benefit of the
approach is that it has relatively modest data requirements: only the
road network (from OSM), its topography (from satellite imagery), and
OD data (from the national census in this case) are
needed, opening up the possibility of deploying the approach in other
cities^[The results are easily reproducible for all UK cities, and can also be reproduced for cities elsewhere given the availability of commuter data. Instructions for reproducing the results are detailed in the **README** file in the R folder of this [Github repository](https://github.com/Hussein-Mahfouz/cycle-networks)]

@@

<!-- For after publishing

^[The results are easily reproducible for all UK cities, and can also be reproduced for cities elsewhere given the availability of commuter data. Instructions for reproducing the results are detailed in this [Github repository](https://github.com/Hussein-Mahfouz/cycle-networks)]. -->

@@

Consideration of these limitations suggest future directions of research.
New datasets and continuously evolving computational (hardware and software)
capabilities should enable the data related issues to be overcome as open
datasets, and our ability to process them, improve.
Plugging-in alternative uptake models could help address the relatively narrow
definition of 'potential' used in this paper, to consider broader social factors.
A promising area of future research in this direction could be 
to integrate a wider range of modes, including e-bikes and e-scooters, into the
analysis. Currently scope for progress in this direction is
partially restricted by the lack of data on the
proliferation of these modes, raising the point that surveys could
replace the broad category of `Bicycle' a range of small modes such as
'pedal cycles' (including tricycles and recumbent cycles), e-bikes
and other forms of micro-mobility.

Despite the rapid growth of these alternative modes, there is little doubt that
the humble bicycle is a key ingredient in the ongoing shift towards active transport.
Recognition of the importance of this shift for improved the health and well-being
the citizens, and the wider challenge to decarbonise the global economy,
has grown with pressures on health and public transport systems during the pandemic.
The success of policies to accelerate cycling uptake depends on a range of
factors including, vitally, the design of the
cycling network for potential cyclists.
The approach presented in this paper provides a strong evidence base,
that considers both cycling potential and social equity,
for designing joined-up and cost-effective strategic cycle networks.
<!-- In tandem with policies to reduce excessive reliance on private cars, evidence-based investment in strategic cycle networks is key to. -->

<!-- I think it would be good to say how others could reproduce the methods in other cities (RL) -->

<!-- (HM) Answer: Done. I added a footnote to the first paragraph in the conclusion linking to the github repo -->

<!-- There should also be links to the literature. -->

<!-- (HM) Answer: There are links to the literature at the end of each thematic section (Calculating Potential Cycling Demand / Routing / Road Segment Prioritization). There is a discussion paragraph in each of them. What additional links are necessary here? -->

@@

>>>>

---
title: A Road Segment Prioritization Approach for Cycling Infrastructure
author:
  - Hussein Mahfouz:
      email: h.mahfouz.19@ucl.ac.uk
      institute: casa
      correspondence: true
  - name: Elsa Arcaute
    institute: casa
  - name: Robin Lovelace
    institute: its
institute:
  - casa: The Centre for Advanced Spatial Analysis, University College London, London, UK
  - its: Institute of Transport Studies, University of Leeds, Leeds, UK

geometry: margin=2cm
bibliography:
  - mybibfile.bib
  - rlbibfile.bib
#linenumbers: true
numbersections: true
abstract: "Understanding the motivators and deterrents to cycling is essential for creating infrastructure that gets more people to adopt cycling as a mode of transport. This paper demonstrates a new approach to support the prioritization of cycling infrastructure and cycling network design, accounting for cyclist preferences and the growing emphasis on 'filtered permeability' and 'Low Traffic Neighborhood' interventions internationally. The approach combines distance decay, route calculation, and network analysis methods to examine where future cycling demand is most likely to arise, how such demand could be accommodated within existing street networks, and how to ensure a fair distribution of investment. Although each of these methods has been applied to cycling infrastructure prioritization in previous research, this is the first time that they have been combined, creating an integrated road segment prioritization approach. The approach, which can be applied to other cities, as shown in the Appendix, is demonstrated in a case study of Manchester, resulting in cycling networks that balance directness against the need for safe and stress-free routes under different investment scenarios. A key benefit of the approach from a policy perspective is its ability to support egalitarian and cost-effective strategic cycle network planning. \\par\\textbf{Keywords:} cycling networks, low-traffic neighborhoods, routing, transport equity"
# keywords: "cycling networks, low-traffic neighborhoods, potential demand, routing"
output:
 # bookdown::github_document2:
   bookdown::pdf_document2:
 # bookdown::word_document2:
      highlight: null   # to remove code highlighting in r chunks
      toc: false
      extra_dependencies: ["subcaption", "longtable", "float", "multirow", "placeins", "multicol"]
      # https://stackoverflow.com/questions/52918716/authors-and-affiliations-in-the-yaml-of-rmarkdown
      pandoc_args:
      - '--lua-filter=extras/scholarly-metadata.lua'
      - '--lua-filter=extras/author-info-blocks.lua'
      keep_tex:  true
editor_options:
  markdown:
    wrap: 72
# elsevier style for referencing (from https://github.com/citation-style-language/styles)
csl: extras/elsevier-harvard.csl
always_allow_html: yes
---

@@

@@

Much research has been done to understand what gets people to cycle.
Segregated cycling infrastructure^[*Segregated cycling infrastructure*
refers to road space that is allocated to cyclists only, with physical
separation to protect cyclists from other modes of transport.] has been
shown to increase cycling uptake [@aldred2019impacts; @goodman2014new;
@marques2015infrastructure], with the separation from motorized
vehicles being key [@winters2011motivators]. Revealed preference of
cyclists shows that they are willing to deviate from the most efficient
routes in order to commute on safer roads [@crane2017longitudinal].
However, such deviations are only considered if they do not considerably
increase route circuitry; behaviour studies have found that the
probability of choosing a route decreases in proportion to its length
relative to the shortest route [@broach2011bicycle; @winters2010far].
Another defining feature for cycling infrastructure is how well
connected it is; cyclists prefer cohesive infrastructure, particularly
when cycling on arterial roads with high levels of motorized traffic
[@stinson2003commuter]. The lack of well-connected cycling
infrastructure is one of the main obstacles to increasing cycling uptake
[@caulfield2012determining]. While direct and cohesive cycling networks
have been shown to positively impact cycling rates, density^[making an
area's bicycle network denser means adding more cycling routes in the
area and thereby giving cyclists more route options.] of the cycling
network is also vital [@schoner2014missing].

@@

\noindent where $d$ and $s$ are the distance and slope associated with each
OD pair, and $\alpha$ and all $\beta$s are parameters calculated by a regression
model on the training data. The square and square-root distance terms
"capture the non-linear impact of distance on the likelihood of
cycling", and interaction terms to capture the combined effect of slope
and distance [@lovelace2017propensity]. Alternative cycling uptake
models could be 'plugged in' to our approach for different contexts or scenarios of change.

@@

@@

This algorithm ensures that the resulting network is connected. It also
satisfies the directness criteria, since links on the weighted shortest
paths are those that have the highest flow passing through them (this is
a result of the routing in Section \@ref(routing).

@@

Given that the "most essential activity entailed in the design of
cycle-friendly infrastructure is developing a cycle network"
[@parkin2018designing], we believe that the approach has great
potential to inform investment in cities such as Manchester where there
is political will to invest in cycling long-term. A benefit of the
approach is that it has relatively modest data requirements: only the
road network (from OSM), its topography (from satellite imagery), and
OD data (from the national census in this case) are
needed, opening up the possibility of deploying the approach in other
cities.^[The results are easily reproducible for all UK cities, and can also be reproduced for cities elsewhere given the availability of commuter data. Instructions for reproducing the results are detailed in the **README** file in the R folder of this [Github repository](https://github.com/Hussein-Mahfouz/cycle-networks)

@@

@@

Consideration of these limitations suggest future directions of research.
New datasets and continuously evolving computational (hardware and software)
capabilities should enable the data related issues to be overcome as open
datasets, and our ability to process them, improve.
Plugging-in alternative uptake models could help address the relatively narrow
definition of 'potential' used in this paper, to consider broader social factors.
A promising area of future research in this direction could be 
to integrate a wider range of modes, including e-bikes and e-scooters, into the
analysis. Currently scope for progress in this direction is
partially restricted by the lack of data on the
proliferation of these modes, raising the point that surveys could
replace the broad category of `Bicycle' with a range of small modes such as
'pedal cycles' (including tricycles and recumbent cycles), e-bikes
and other forms of micro-mobility.

Despite the rapid growth of these alternative modes, there is little doubt that
the humble bicycle is a key ingredient in the ongoing shift towards active transport.
Recognition of the importance of this shift for improved health and well-being
of citizens, and the wider challenge to decarbonise the global economy,
has grown with pressures on health and public transport systems during the pandemic.
The success of policies to accelerate cycling uptake depends on a range of
factors including, vitally, the design of the
cycling network for potential cyclists.
The approach presented in this paper provides a strong evidence base,
that considers both cycling potential and social equity,
for designing joined-up and cost-effective strategic cycle networks.

\clearpage

@@

<div id="refs"></div>

# (APPENDIX) Appendix {-} 
\clearpage
# Appendix: Reproducing the results for other cities

To reproduce the results presented for other cities in the UK there are a few computing pre-requisites:

- A reasonably powerful computer, e.g. with 8 GB RAM
- The statistical programming language R installed (we recommend running it in the RStudio editor)
- The source code of the paper repository, which can be download from this [Github repository](https://github.com/Hussein-Mahfouz/cycle-networks)]

```{r, eval=FALSE, echo=FALSE}
# run these lines to update the snapshot
required_packages = renv::dependencies()
renv::snapshot()
```

To ensure you have the necessary packages installed, open the `cycle-networks.Rproj` file in RStudio and run the following commands to ensure you have the necessary packages installed:

```{r, eval=FALSE}
install.packages("renv")
renv::restore()
```

The `build.R` script contains all of the necessary steps to reproduce the results for any city in the UK.
Open this file with the following command and run the code line-by-line.

```{r, eval=FALSE}
file.edit("R/build.R")
```

<!-- Todo: make the .zip download work for anyone, e.g. by uploading the data to the osf.io website alongside the preprint. -->

You can select a city to build by executing the following command:

```{r}
chosen_city <- "Leeds"
```

Replacing `Leeds` with any other city will make the script work for that city.
Note: this only works for Local Authority names in England and Wales listed below.

In this script, you choose which city you wish to run the analysis from
this list of available towns and cities:

    ##   [1] "Barnsley"             "Basildon"             "Basingstoke"
    ##   [4] "Bath"                 "Bedford"              "Birkenhead"
    ##   [7] "Birmingham"           "Blackburn"            "Blackpool"
    ##  [10] "Bolton"               "Bournemouth"          "Bracknell"
    ##  [13] "Bradford"             "Brighton and Hove"    "Bristol"
    ##  [16] "Burnley"              "Burton upon Trent"    "Bury"
    ##  [19] "Cambridge"            "Cardiff"              "Carlisle"
    ##  [22] "Chatham"              "Chelmsford"           "Cheltenham"
    ##  [25] "Chester"              "Chesterfield"         "Colchester"
    ##  [28] "Coventry"             "Crawley"              "Darlington"
    ##  [31] "Derby"                "Doncaster"            "Dudley"
    ##  [34] "Eastbourne"           "Exeter"               "Gateshead"
    ##  [37] "Gillingham"           "Gloucester"           "Grimsby"
    ##  [40] "Guildford"            "Halifax"              "Harlow"
    ##  [43] "Harrogate"            "Hartlepool"           "Hastings"
    ##  [46] "Hemel Hempstead"      "High Wycombe"         "Huddersfield"
    ##  [49] "Ipswich"              "Kingston upon Hull"   "Leeds"
    ##  [52] "Leicester"            "Lincoln"              "Liverpool"
    ##  [55] "London"               "Luton"                "Maidstone"
    ##  [58] "Manchester"           "Mansfield"            "Middlesbrough"
    ##  [61] "Milton Keynes"        "Newcastle upon Tyne"  "Newcastle-under-Lyme"
    ##  [64] "Newport"              "Northampton"          "Norwich"
    ##  [67] "Nottingham"           "Nuneaton"             "Oldham"
    ##  [70] "Oxford"               "Peterborough"         "Plymouth"
    ##  [73] "Poole"                "Portsmouth"           "Preston"
    ##  [76] "Reading"              "Redditch"             "Rochdale"
    ##  [79] "Rotherham"            "Salford"              "Scunthorpe"
    ##  [82] "Sheffield"            "Shrewsbury"           "Slough"
    ##  [85] "Solihull"             "South Shields"        "Southampton"
    ##  [88] "Southend-on-Sea"      "Southport"            "St Albans"
    ##  [91] "St Helens"            "Stevenage"            "Stockport"
    ##  [94] "Stockton-on-Tees"     "Stoke-on-Trent"       "Sunderland"
    ##  [97] "Sutton Coldfield"     "Swansea"              "Swindon"
    ## [100] "Telford"              "Wakefield"            "Walsall"
    ## [103] "Warrington"           "Watford"              "West Bromwich"
    ## [106] "Weston-Super-Mare"    "Wigan"                "Woking"
    ## [109] "Wolverhampton"        "Worcester"            "Worthing"
    ## [112] "York"

\newpage

## Birmingham

\subsubsection{Potential Demand}

```{r potdemhistogramsBirmingham, fig.cap="Distribution of Potential Cycling Demand", out.width="30%", fig.show='hold', echo=FALSE}
knitr::include_graphics(c(
  "data/Birmingham/Plots/histogram_distance_all_vs_cycling.png",
  "data/Birmingham/Plots/histogram_distance_all_vs_cycling_potential.png",
  "data/Birmingham/Plots/histogram_distance_cycling_potential_vs_current.png"
))
```

```{r desirefacetcyclingBirmingham, fig.cap="Current and Potential Cycling Demand", out.width="80%", fig.pos="H", fig.align="center", echo=FALSE}
knitr::include_graphics("data/Birmingham/Plots/desire_facet_cycling.png")
```

\clearpage

\subsubsection{Routing Cycling Flows}

```{r flowsfacetunweightedBirmingham, fig.cap="Flow Results Based on Unweighted Shortest Paths (Birmingham)", out.width="75%", fig.show='hold', fig.align = "center", echo=FALSE}
knitr::include_graphics("data/Birmingham/Plots/flows_facet_unweighted_Birmingham.png")
```

```{r flowsfacetweightedBirmingham, fig.cap="Flow Results Based on Weighted Shortest Paths (Birmingham)", out.width="75%", fig.show='hold', fig.align = "center", echo=FALSE}
knitr::include_graphics("data/Birmingham/Plots/flows_facet_weighted_Birmingham.png")
```

\clearpage

\subsubsection{Community Detection}

```{r communitiesBirmingham, fig.cap="Communities Based on Potential Cycling Demand (Birmingham)", out.width="90%", fig.show='hold', fig.align = "center", echo=FALSE}
knitr::include_graphics("data/Birmingham/Plots/communities_alternative_Birmingham.png")
```

\subsubsection{Network Expansion Algorithms}

```{r growthtotalBirmingham, fig.cap="Comparing Overall (Dashed) and Community Level Person-Km Satisfied (Birmingham)", out.width="45%", fig.show='hold', fig.pos="H", fig.align = "center", echo=FALSE}
knitr::include_graphics(c(
  "data/Birmingham/Plots/Growth_Results/growth_utilitarian_satisfied_km_both_flow_column.png",
  "data/Birmingham/Plots/Growth_Results/growth_egalitarian_satisfied_km_both_flow_column.png"
))
```

```{r componentsandGCCBirmingham, fig.cap="Network Characteristics", out.width="45%", fig.show='hold', fig.pos="H", fig.align = "center", echo=FALSE}
knitr::include_graphics(c(
  "data/Birmingham/Plots/Growth_Results/growth_util_egal_components_number_comparisonBirmingham.png",
  "data/Birmingham/Plots/Growth_Results/growth_util_egal_components_gcc_comparisonBirmingham.png"
))
```

```{r growth3MapandBarBirmingham, fig.cap="Road Segment Priority (left), disaggregated by road type (right) - Egalitarian Growth", out.width="45%", fig.show='hold', fig.align="center", echo=FALSE}
knitr::include_graphics(c(
  "data/Birmingham/Plots/Growth_Results/growth_egalitarian_priority_all_FLOW.png"#,
 # "data/Birmingham/Plots/Growth_Results/growth_egalitarian_investment_highways_flow.png"
))
```

\clearpage

## Leeds

\subsubsection{Potential Demand}

```{r potdemhistogramsLeeds, fig.cap="Distribution of Potential Cycling Demand", out.width="30%", fig.show='hold', echo=FALSE}
knitr::include_graphics(c(
  "data/Leeds/Plots/histogram_distance_all_vs_cycling.png",
  "data/Leeds/Plots/histogram_distance_all_vs_cycling_potential.png",
  "data/Leeds/Plots/histogram_distance_cycling_potential_vs_current.png"
))
```

```{r desirefacetcyclingLeeds, fig.cap="Current and Potential Cycling Demand", out.width="80%", fig.pos="H", fig.align="center", echo=FALSE}
knitr::include_graphics("data/Leeds/Plots/desire_facet_cycling.png")
```

\clearpage

\subsubsection{Routing Cycling Flows}

```{r flowsfacetunweightedLeeds, fig.cap="Flow Results Based on Unweighted Shortest Paths (Leeds)", out.width="75%", fig.show='hold', fig.align = "center", echo=FALSE}
knitr::include_graphics("data/Leeds/Plots/flows_facet_unweighted_Leeds.png")
```

```{r flowsfacetweightedLeeds, fig.cap="Flow Results Based on Weighted Shortest Paths (Leeds)", out.width="75%", fig.show='hold', fig.align = "center", echo=FALSE}
knitr::include_graphics("data/Leeds/Plots/flows_facet_weighted_Leeds.png")
```

\clearpage

\subsubsection{Community Detection}

```{r communitiesLeeds, fig.cap="Communities Based on Potential Cycling Demand (Leeds)", out.width="90%", fig.show='hold', fig.align = "center", echo=FALSE}
knitr::include_graphics("data/Leeds/Plots/communities_alternative_Leeds.png")
```

\subsubsection{Network Expansion Algorithms}

```{r growthtotalLeeds, fig.cap="Comparing Overall (Dashed) and Community Level Person-Km Satisfied (Leeds)", out.width="45%", fig.show='hold', fig.pos="H", fig.align = "center", echo=FALSE}
knitr::include_graphics(c(
  "data/Leeds/Plots/Growth_Results/growth_utilitarian_satisfied_km_both_flow_column.png",
  "data/Leeds/Plots/Growth_Results/growth_egalitarian_satisfied_km_both_flow_column.png"
))
```

```{r componentsandGCCLeeds, fig.cap="Network Characteristics", out.width="45%", fig.show='hold', fig.pos="H", fig.align = "center", echo=FALSE}
knitr::include_graphics(c(
  "data/Leeds/Plots/Growth_Results/growth_util_egal_components_number_comparisonLeeds.png",
  "data/Leeds/Plots/Growth_Results/growth_util_egal_components_gcc_comparisonLeeds.png"
))
```

```{r growth3MapandBarLeeds, fig.cap="Road Segment Priority (left), disaggregated by road type (right) - Egalitarian Growth", out.width="45%", fig.show='hold', fig.align="center", echo=FALSE}
knitr::include_graphics(c(
  "data/Leeds/Plots/Growth_Results/growth_egalitarian_priority_all_FLOW.png",
  "data/Leeds/Plots/Growth_Results/growth_egalitarian_investment_highways_flow.png"
))
```

\clearpage

## Nottingham

\subsubsection{Potential Demand}

```{r potdemhistogramsNottingham, fig.cap="Distribution of Potential Cycling Demand", out.width="30%", fig.show='hold', echo=FALSE}
knitr::include_graphics(c(
  "data/Nottingham/Plots/histogram_distance_all_vs_cycling.png",
  "data/Nottingham/Plots/histogram_distance_all_vs_cycling_potential.png",
  "data/Nottingham/Plots/histogram_distance_cycling_potential_vs_current.png"
))
```

```{r desirefacetcyclingNottingham, fig.cap="Current and Potential Cycling Demand", out.width="80%", fig.pos="H", fig.align="center", echo=FALSE}
knitr::include_graphics("data/Nottingham/Plots/desire_facet_cycling.png")
```

\clearpage

\subsubsection{Routing Cycling Flows}

```{r flowsfacetunweightedNottingham, fig.cap="Flow Results Based on Unweighted Shortest Paths (Nottingham)", out.width="75%", fig.show='hold', fig.align = "center", echo=FALSE}
knitr::include_graphics("data/Nottingham/Plots/flows_facet_unweighted_Nottingham.png")
```

```{r flowsfacetweightedNottingham, fig.cap="Flow Results Based on Weighted Shortest Paths (Nottingham)", out.width="75%", fig.show='hold', fig.align = "center", echo=FALSE}
knitr::include_graphics("data/Nottingham/Plots/flows_facet_weighted_Nottingham.png")
```

\clearpage

\subsubsection{Community Detection}

```{r communitiesNottingham, fig.cap="Communities Based on Potential Cycling Demand (Nottingham)", out.width="90%", fig.show='hold', fig.align = "center", echo=FALSE}
knitr::include_graphics("data/Nottingham/Plots/communities_alternative_Nottingham.png")
```

\subsubsection{Network Expansion Algorithms}

```{r growthtotalNottingham, fig.cap="Comparing Overall (Dashed) and Community Level Person-Km Satisfied (Nottingham)", out.width="45%", fig.show='hold', fig.pos="H", bifig.align = "center", echo=FALSE}
knitr::include_graphics(c(
  "data/Nottingham/Plots/Growth_Results/growth_utilitarian_satisfied_km_both_flow_column.png",
  "data/Nottingham/Plots/Growth_Results/growth_egalitarian_satisfied_km_both_flow_column.png"
))
```

```{r componentsandGCCNottingham, fig.cap="Network Characteristics", out.width="45%", fig.show='hold', fig.pos="H", fig.align = "center", echo=FALSE}
knitr::include_graphics(c(
  "data/Nottingham/Plots/Growth_Results/growth_util_egal_components_number_comparisonNottingham.png",
  "data/Nottingham/Plots/Growth_Results/growth_util_egal_components_gcc_comparisonNottingham.png"
))
```

```{r growth3MapandBarNottingham, fig.cap="Road Segment Priority (left), disaggregated by road type (right) - Egalitarian Growth", out.width="45%", fig.show='hold', fig.align="center", echo=FALSE}
knitr::include_graphics(c(
  "data/Nottingham/Plots/Growth_Results/growth_egalitarian_priority_all_FLOW.png",
  "data/Nottingham/Plots/Growth_Results/growth_egalitarian_investment_highways_flow.png"
))
```

\clearpage
